---
title: 'RWorksheet #5'
author: "Grace Anne E. Capanang"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1a. Plot the data using a bar graph. Write the codes and copy the result.

```{r}
Year <- c("1st", "2nd", "3rd", "4th")
Year
numberOfEnrolees <- c(80, 75, 70, 60)
numberOfEnrolees

barplot(numberOfEnrolees,                                       # Add labels to barplot
        names.arg = Year,
        col = "pink")
```

#1b. Using the same table, label the barchart with (1) Title = ” Enrollment of BS Computer Science, (2) horizontal axis = “Curriculum Year” and (3) vertical axis = “number of students”.

```{r}
barplot(numberOfEnrolees,                                       
        names.arg = Year,
        main = "Enrollment of BS Computer Science",
        xlab = "Curriculum Year",
        ylab = "number of students",
        col = "dark blue"
)
```

#2a. The monthly income of De Jesus family was spent on the following:
#60% on Food, 10% on electricity, 5% for savings, and 25% for other miscellaneous expenses.

#Create a table for the above scenario. Write the codes and its result.

```{r}
expenses <- c("Food", "Electricity", "Savings", "Miscelleneous Expenses")
howMuch <- c(60, 10, 5, 25)

Expenses <- data.frame(
  expenses,
  howMuch
)
Expenses

tableExpenses <- table(Expenses)
tableExpenses
```

#2b.  Plot the data using a pie chart. Add labels, colors and legend. Write the codes and its result.

```{r}
library(scales)

equation <- round(howMuch/sum(howMuch) * 1, 2)
percentage <- percent(equation)
percentage

pieData <- pie(howMuch,
                main = "Month Data",
                col = rainbow(4),
                labels = percentage,
                cex = 0.8)
pieData

legend(1,1, 
       c("Food", "Electricity", "Savings", "Miscellaneous expenses"),
       cex = 0.5, 
       fill = rainbow(4))
```

#3a. Open the mtcars dataset.Create a simple histogram specifically for mpg (miles per gallon) variable.Use $ to select the mpg only. Write the codes and its result.

```{r}
data(mtcars)

mpgHistogram <- hist(mtcars$mpg)
mpgHistogram
```


#3b  Colored histogram with different number of bins.

```{r}
hist(mtcars$mpg, breaks=12, col="red")
coloredMpg <- hist(mtcars$mpg, breaks=12, col="red")

```

```{r}
difNumBins <- hist(mtcars$mpg, breaks=7, col="red")

```

#3c.  Adding a Normal Curve

```{r}
x <- mtcars$mpg
h<-hist(x, breaks=10, col="red", xlab="Miles Per Gallon",
        main="Histogram with Normal Curve")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)
```

#4a. Open the iris dataset. Create a subset for each species. Write the codes and its result.

```{r}

data("iris")

setosaSubset <- subset(iris, Species == 'setosa' )
setosaSubset
versicolorSubset <- subset(iris, Species == 'versicolor' )
versicolorSubset
virginicaSubset <- subset(iris, Species == 'virginica' )
virginicaSubset
```

#4b. Get the mean for every characteristics of each species using colMeans(). Write the codes and its result.

```{r}
setosa <- colMeans(setosaSubset[sapply(setosaSubset,is.numeric)])
setosa

versicolor <- colMeans(versicolorSubset[sapply(versicolorSubset,is.numeric)])
versicolor

virginica <- colMeans(virginicaSubset[sapply(virginicaSubset,is.numeric)])
virginica
```

#4c. Combine all species by using rbind().

```{r}
rbindIrisData <- rbind(setosa, versicolor, virginica)
rbindIrisData
```

#4d. From the data in 4-c: Create the barplot(). Write the codes and its result.

```{r}
barplot(rbindIrisData, 
        beside = TRUE, 
        main = "Iris Data",
        xlab = "Characteristics",
        ylab = "Mean Scores",
        col = c("blue", "green", "yellow"),
        
)
```





