---
title: 'RWorksheet #7'
author: "Grace Anne Capanang"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Basic Statistics 

1. Create a data frame for the table below.

```{r}
Students <- seq (1, 10)
PreTest <- c (55,54,47,57,51,61,57,54,63,58)
PostTest <- c (61,60,56,63,56,63,59,56,62,61)

studentsGrades <- data.frame(
  Students,
  PreTest,
  PostTest)
studentsGrades
```

1a.  Compute the descriptive statistics using different packages (Hmisc and pastecs).
Write the codes and its result.

```{r}
 library(Hmisc)
 library(pastecs)

#descriptive statistic using Hmisc package
hmiscStat <- describe(studentsGrades)
hmiscStat

#decriptive statistic using the pastecs package
pastecsStat <- stat.desc(studentsGrades)
pastecsStat
```

2. The Department of Agriculture was studying the effects of several levels of a fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an ordered factor.

```{r}
fertilizerLevel <- factor(c(10, 10, 10, 20, 20, 50, 10, 20, 10, 50, 20, 50, 20, 10),
                    ordered = TRUE)
fertilizerLevel
class(fertilizerLevel)

orderFertlizerLevel <- sort (fertilizerLevel)
orderFertlizerLevel
```

#describe the result:
#the result outputs the values in ascending order, where the levels shows the inequality (<) of the values.


3a. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” , “l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense. What is the best way to represent this in R?

```{r}
exerciseLevels <- c("l", "n", "n", "i", "l", "l", "n", "n", "i", "l")
exerciseLevels

factorLevels <- factor(exerciseLevels)
factorLevels

levels(factorLevels) <- c("intense", "light", "none")
factorLevels
```

4. Sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as:
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld", "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt", "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw", "vic", "vic", "act")

4a. Apply the factor function and factor level. Describe the results.

```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")
state

factoredDataStateAccountants <- factor(state)
factoredDataStateAccountants
#describe the result
#the factor function in this item arranged the values of the variable state alphabetically and 
#sorted them or leveled them.

levelfactoredStateAccountants <- levels(factoredDataStateAccountants)
levelfactoredStateAccountants
#describe the result
#the result outputs the sorted values from previous number in character form because of the quotation 
#marks (""), and the 'Levels' that can be seen in the output from factor function is now gone. 

```

5. From #4 - continuation:
Suppose we have the incomes of the same tax accountants in another vector (in suitably large units of money). 

```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
incomes
```

5a. Calculate the sample mean income for each state we can now use the special function tapply():

```{r}
incmeans <- tapply(incomes, factoredDataStateAccountants, mean)
incmeans
```

b. Copy the results and interpret.
# the tapply function in this item calculated the mean of the factored State accountants' income. 


6. Calculate the standard errors of the state income means (refer again to number 3). What is the standard error? Write the codes.

```{r}
stdError <- sqrt(var(incmeans)/length(incmeans))
stdError
```

#another method for #6

```{r}
incMeansSD <- sqrt(var(incmeans)) #mean
incMeansSD
sd(incmeans)

length(incmeans) #size

standardError <- incMeansSD / sqrt(8) #standard error
standardError
```

After this assignment, the standard errors are calculated by:

#incster <- tapply(incomes, factoredDataStateAccountants, stdError)
#incster


6b. Interpret the result.
#in this item there is an error, but the standard error of the factored State accountants' income is produce in the output in Rfile.
#output is:
#act      nsw       nt      qld       sa      tas      vic       wa 
#1.500000 4.310195 4.500000 4.106093 2.738613 0.500000 5.244044 2.657536 


7. Use the titanic dataset.
a. subset the titatic dataset of those who survived and not survived. Show the codes and its result.

```{r}
data(Titanic)

titanicDataFrame <- data.frame(Titanic)

titanicSurvived <- subset(titanicDataFrame, Survived == "Yes")
titanicSurvived

titanicDidntSurvived <- subset(titanicDataFrame, Survived == "No")
titanicDidntSurvived

```

8. The data sets are about the breast cancer Wisconsin. The samples arrive periodically as Dr. Wolberg reports his clinical cases. The database therefore reflects this
chronological grouping of the data. You can create this dataset in Microsoft Excel.

8a. describe what is the dataset all about.
#the dataset is about a database of Dr. Wolberg's breast cancer clinical cases samples.


8b. Import the data from MS Excel. Copy the codes.

```{r}
getwd()
library(readxl)
library(plotrix)


brstCancerData <- read_excel('C:\\ANOTHER\\NEECHAN\\PracticeGit\\#3b, 4, 5\\Worksheet 7\\breastCancer.xlsx')
brstCancerData

brstCancerDataFrame <- data.frame(brstCancerData)
brstCancerDataFrame
```

8c1. Standard error of the mean for clump thickness.

```{r}

clumpThickness <- subset(brstCancerDataFrame, select = CL..thickness)
clumpThickness
std.error(clumpThickness)

std.error(brstCancerDataFrame$CL..thickness) #trying another method
```

8c.2 Coefficient of variability for Marginal Adhesion.

```{r}
marginalAdhessionCV <- sd(brstCancerDataFrame$Marg..Adhesion) / mean(brstCancerDataFrame$Marg..Adhesion) * 100
marginalAdhessionCV

```

8c.3 Number of null values of Bare Nuclei.

```{r}
var <- subset(brstCancerDataFrame, select = Bare..Nuclei)
var

sum(is.na(var))
```

8c.4 Mean and standard deviation for Bland Chromatin.

```{r}
blChromatinSD <- sqrt(var(brstCancerDataFrame$Bl..Cromatin))
blChromatinSD

blChromatinMean <- mean(brstCancerDataFrame$Bl..Cromatin)
blChromatinMean
```

8c.5 Confidence interval of the mean for Uniformity of Cell Shape.

```{r}
s = length(brstCancerDataFrame$Cell.Shape) #size
s

meanCS <- mean(brstCancerDataFrame$Cell.Shape) #mean
meanCS

csSD <- sqrt(var(brstCancerDataFrame$Cell.Shape)) #standard deviation
csSD

sd(brstCancerDataFrame$Cell.Shape) #another method for sd

standardError <- csSD / sqrt(s) #standard error
standardError

alpha = 0.05
degrees_of_freedom = s - 1
t_score = qt(p=alpha/2, df=degrees_of_freedom,lower.tail=F)
print(t_score)

marginError <- t_score * standardError #margin error
marginError

lowerBound <- meanCS - marginError
lowerBound

upperBound <- meanCS + marginError
upperBound

#lower and upper bounds of confidence interval
lowerBound
upperBound

```

8d. How many attributes?
```{r}
attributesNumber <- attributes(brstCancerData)
attributesNumber
```


8e. Find the percentage of respondents who are malignant. Interpret the results.

```{r}
subsetting <- subset(brstCancerDataFrame, Class=="malignant")
subsetting

classVar <- (brstCancerDataFrame$Class)
classVar

malignant <- length(subsetting)
malignant
variableClass <- length(classVar)
variableClass

options (digits = 4)
percentage <- (malignant * 100) / variableClass
percentage
```

#In this item we got the number of patients whose their type of cancer is malignant by subsetting.
#And then we got the percentage of the malignant patients from the subsetted variable multiply to 100 and divided by the overall number of respondents.

9. Export the data abalone to the Microsoft excel file. Copy the codes.

```{r}
library(AppliedPredictiveModeling)
data(abalone)
library(xlsx)
write.xlsx(abalone, "abalone.xlsx")

View(abalone)
head(abalone)
summary(abalone)
```
