---
title: "Worksheet 2"
author: "Grace Anne E. Capanang"
date: "2022-10-07"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions:
• Use RStudio or the RStudio Cloud accomplish this worksheet. + Save the R script as
RWorksheet_lastname#2.R.
• Create your own GitHub repository and push the R script as well as this pdf worksheet
to your own repo.

Accomplish this worksheet by answering the questions being asked and writing the code
manually.

## Using Vectors

1. Create a vector using: operator
a. Sequence from -5 to 5. 

``` {r five, error=TRUE}
    five <- -5:5
    five
```
The output produces values from numbers -5 to 5.


b. x <- 1:7. What will be the value of x?

```{r x, error=TRUE}
    x <- 1:7
    x
```
The value of x are numbers from 1 to 7 in sequence, that is, 1, 2, 3, 4, 5, 6, 7.


2.* Create a vector using seq() function a. seq(1, 3, by=0.2) # specify step size Write the R code and its output. Describe the output.

```{r jump, error=TRUE}
    jump <- seq(1, 3, by = 0.2)
    jump

```
The output is numbers from 1 to 3 sequently with a decimal 0.2 in between, that is 1.0 1.2 1.4 1.6 1.8 2.0 2.2 2.4 2.6 2.8 3.0.





3. A factory has a census of its workers. There are 50 workers in total. The following
list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.

```{r workersAges, error=TRUE}
    workersAges <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,22, 37, 34, 19, 20, 57, 49, 
50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 
54, 58, 26,18)
    workersAges
```



3a. Access 3rd element, what is the value?

```{r ThirdElement, error=TRUE}
    ThirdElement <- workersAges[3]
    ThirdElement
    
```
The value in the 3rd element is 22.



3b. Access 2nd and 4th element, what are the values?

```{r SecondElement, FourthElement, SecondFourth, error=TRUE}
    SecondElement <- workersAges[2]
    SecondElement
    FourthElement <- workersAges[4]
    FourthElement
    SecondFourth <- c(SecondElement, FourthElement)
    SecondFourth
```
The value in the 2nd element is 28 and in the fourth element is 36.

4. *Create a vector x <- c("first"=3, "second"=0, "third"=9). Then named the vector, names(x).
a. Print the results. Then access x[c("first", "third")].
Describe the output.

``` {r x1, error=TRUE}
    x1 <- c("first"=3, "second"=0, "third"=9)
    names(x1)
    x1[c("first", "third")]
```

The program output the assigned integer value in the string named "first" and "third" using square brackets [] means accessing through index.

5. Create a sequence x from -3:2.
a. Modify 2nd element and change it to 0

``` {r x2, error=TRUE}
    x2 <- -3:2
    x2
    x2[2] = 0
    x2
```
The program first produces an output of integers from -3 to 2 in sequence, and when we used an indexing using square brackets [] that access the element value we want to change which is the second position in the index, we modified the original value in that position which is -2 and changed it to 0. Thus, afterwards when prompt for the elements inside the x the second value is now 0.




6. *The following data shows the diesel fuel purchased by Mr. Cruz.

a. Create a data frame for month, price per liter (php) and purchase-quantity (liter).
Write the codes.

``` {r DieselPurchased, error=TRUE} 

Month = c("Jan", "Feb", "March","April", "May","June")
  PricePerLiter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
  PurchaseQuantity <- c(25, 30, 40, 50, 10, 45)

  DieselPurchased <- data.frame (
  Month, 
  PricePerLiter, 
  PurchaseQuantity 
  )
  DieselPurchased
```
  

b. What is the average fuel expenditure of Mr. Cruz from Jan to June? Note: Use weighted.mean(liter, purchase)

```{r Mean, error=TRUE}
Month = c("Jan", "Feb", "March","April", "May","June")
  PricePerLiter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
  PurchaseQuantity <- c(25, 30, 40, 50, 10, 45)
 Mean <- weighted.mean(PricePerLiter, PurchaseQuantity)
 Mean
```



7. R has actually lots of built-in datasets. For example, the rivers data “gives the lengths
(in miles) of 141 “major” rivers in North America, as compiled by the US Geological
Survey”.

a. Type “rivers” in your R console. Create a vector data with 7
elements, containing the number of elements (length) in rivers,
their sum (sum), mean (mean), median (median), variance (var)
standard deviation (sd), minimum (min) and maximum (max).

``` {r data, error=TRUE}
    rivers

    data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers),var(rivers), sd(rivers), 
min(rivers),max(rivers))
    data
```
b. What are the results? 
The results displayed a number answers needed with the function lenght, sum, mean, median, var, sd, min, and max used with the elements of rivers. 

8. The table below gives the 25 most powerful celebrities and their annual pay as rank.

a. Create vectors according to the above table. Write the codes.

```{r CelebrityAnnualPay, error=TRUE}
PowerRanking <- 1:25
    CelebrityName <- c("Tom Cruise","Rolling Stones", "Oprah Winfrey","U2","Tiger Woods", 
                       "Steven Spielberg","Howarf Stern","50 Cent","Cast of the Sopranos","Dan Brown",
                       "Bruce Springsteen", "Donald Trump","Muhammand Ali","Paul McCartney",
                       "George Lucas", "Elton John","David Letterman","Phil Mickelson", "J.K Rowling",
                       "Bradd Pitt", "Peter Jackson","Dr.Phil McGraw","Jay Lenon","Celine Dion",
                       "Kobe Bryan")
    Pay <- c(67, 90,225,110,90,332,302,41,52,88,55,44,55,40,233,34,40,47,75,25,39,45,32,40,31)
    
CelebrityAnnualPay <- data.frame(
      PowerRanking, 
      CelebrityName,
      Pay
    )
    CelebrityAnnualPay
```
     
b. Modify the power ranking and pay of J.K. Rowling. Change power ranking to 15 andpay to 90. Write the codes and its output.
 
```{r , error=TRUE}
CelebrityAnnualPay [19, "PowerRanking"] = 15
      CelebrityAnnualPay[19, "Pay"] = 90
      CelebrityAnnualPay
```


c. Interpret the data.
The data was accessed and changed by: (1)declaring the object name of the data frame, (2) using square brackets accessing the rank number,(3) by the vector name where the values we want to change, and lastly by declaring the object name again to access the modified data. JK Rowling's rank was changed from 19 to 15 and her annual pay was changed from 75 to 90.


