---
title: 'Worksheet #4'
author: "Grace Anne E. Capanang"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#1. The table below shows the data about shoe size and height. Create a data frame..

```{r}
ShoeSize <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 
              11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)
ShoeSize

Height <- c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 
            72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)
Height

Gender <- rep(c("F", "M", "F", "M", "F", "M", "F", "M", "M", "F", "M", "F", "M", "F", "M"), 
              c(4, 1, 3, 1, 1, 1, 1, 2, 2, 2, 1, 2, 2, 1, 4))
Gender

ShoeCustomersProfile <- data.frame (
  ShoeSize,
  Height,
  Gender
)
ShoeCustomersProfile

```

#1a. Describe the data.

#1b. Find the mean of shoe size and height of the respondents.
Copy the codes and results.

```{r}
shoeSizeMean <- mean(ShoeSize)
shoeSizeMean
heightMean <- mean(Height)
heightMean
```

#c. Is there a relationship between shoe size and height? Why?

```{r}
maleOnes <- subset(ShoeCustomersProfile, Gender == "M")
maleOnes
maleHeightMean <- mean(maleOnes$Height)
maleHeightMean
maleShoeSizeMean <- mean (maleOnes$ShoeSize)
maleShoeSizeMean


FemaleOnes <- subset(ShoeCustomersProfile, Gender == "F")
FemaleOnes
FemaleHeightMean <- mean(FemaleOnes$Height)
FemaleHeightMean
FemaleShoeSizeMean <- mean (FemaleOnes$ShoeSize)
FemaleShoeSizeMean

# The result of the code above outputs the mean of each gender's height and shoe size. 
#For Male,the shoe size' mean is 10.9, and the height's mean is 71.4. 
#Meanwhile for Female, the shoe size' mean is 7.85, and the height's mean is 65.6. ano konek sa question.

# I filter shoe sizes, one is with equal or less than 9 and the other one is sizes greater than nine. 
#It shows that people with short height have smaller shoe size meanwhile those taller have bigger size. 

sampleSmallShoeSize <- subset(ShoeCustomersProfile, ShoeSize <= 9)
sampleSmallShoeSize
smallSizeMean <- mean(sampleSmallShoeSize$ShoeSize)
smallSizeMean
sampleSmallHeightMean <- mean(sampleSmallShoeSize$Height)
sampleSmallHeightMean

sampleBigShoeSize <- subset(ShoeCustomersProfile, ShoeSize > 9)
sampleBigShoeSize
smallBigMean <- mean(sampleBigShoeSize$ShoeSize)
smallBigMean
sampleBigHeightMean <- mean(sampleBigShoeSize$Height)
sampleBigHeightMean
```

#2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.

```{r}
months_vector <- c("March","April","January","November","January",
            "September","October","September","November","August",
            "January","November","November","February","May","August","July","December","August",
            "August","September","November","February","April")

months_vector

factor_months_vector <- factor(months_vector)
factor_months_vector
```

#3. Then check the summary() of the months_vector and factor_months_vector. Interpret the results of both vectors. Are they both equally useful in this case?

```{r}
monthsSummary <- summary(months_vector)
monthsSummary

factoredMonthsSummary <- summary(factor_months_vector)
factoredMonthsSummary
```

#4. Create a vector and factor for the table below.

```{r}
Direction <- c("East", "West", "North")
Direction
Frequency <- c(1, 4, 3)
Frequency

factoredDirection <- factor(Direction)
factoredDirection
factoredFrequency <- factor(Frequency)
factoredFrequency

new_order_data <- factor(Direction,levels = c("East","West","North"))
print(new_order_data)
```

#5. Enter the data below in Excel with file name = import_march.csv.  Import the excel file into the Environment Pane using read.table() function. Write the code.

```{r}

readTable <- read.table("C:\\Users\\User\\OneDrive\\Documents\\import_march.csv", header=TRUE, 
                        sep = ",")
readTable

readFile <- read.csv("C:\\Users\\User\\OneDrive\\Documents\\import_march.csv")
View(readFile)
```

